Effects on projectivity ratings by Embedding Operator and Trigger --- \newline Data Analysis

### 2022-11-18 materials-lisa/analysis/3_projection-across-operators/analysis.Rnw
try this model

\newpage
\section{Data Overview and Statistical Summaries}
\subsection{Distribution of projectivity ratings by operator:}
<<project-by-op-distr, echo = FALSE>>=
data_all %>% 
  # mutate(verb = fct_reorder(cond, as.numeric(dataf$response), .fun = 'mean')) %>%
  ggplot(aes(x = projective, group = op)) +
  facet_grid(rows = vars(op)) +
  geom_histogram(binwidth = .01, fill = "lightblue") +
  # coord_flip() +
  xlab("") +
  ylab("") +
  labs(title = "")+
  theme_bw()
  # scale_fill_brewer(palette = "Blues")
@

@@

proj_means_op %>% mutate(op = fct_reorder(op, Mean, 
                                         .fun = mean)) %>% 
  ggplot(aes(x = op, y=Mean, color = op)) +
  # coord_cartesian(ylim = c(0,1)) +
  geom_point(aes(shape = op), size = 4) + 
  scale_shape_manual(values = c("M", "N", "Q", "C")) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=0.1) +
  geom_line() + 
  labs(title = "Mean projectivity by operator")+
  theme_bw() +
  scale_color_brewer(palette = "PRGn")
@
\noindent The following generalizations emerge:
\begin{itemize}
  \item Conditionals have the highest projectivity ratings
  \item Projectivity ratings for questions are higher than those for modals and negation, but lower than those for conditionals
  \item Modals and negation have the lowest projectivity ratings
  \item The ratings for negation look a little higher than for modals, but error bars overlap
\end{itemize}

@@

\newpage
\subsection{Means and confidence intervals for projectivity rating by verb:}
<<summary-v, echo = FALSE, message=FALSE, cache=TRUE, fig.width=14, fig.height=7>>=
# load helper functions
source('../../../results/main/helpers.R')

@@

% \section{Exploring a couple of models}
% \subsection{Linear, frequentist}
% Let's try a linear model first, and check error distributions.
%

>>>>

\newpage
\section{Data Overview and Statistical Summaries}
\subsection{Distribution of projectivity ratings by operator:}
<<project-by-op-distr, echo = FALSE>>=
library(ggplot2)
data_all %>% 
  # mutate(verb = fct_reorder(cond, as.numeric(dataf$response), .fun = 'mean')) %>%
  ggplot(aes(x = projective, group = op)) +
  facet_grid(rows = vars(op)) +
  geom_histogram(binwidth = .01, fill = "lightblue") +
  # coord_flip() +
  xlab("") +
  ylab("") +
  labs(title = "")+
  theme_bw()
  # scale_fill_brewer(palette = "Blues")
@

@@

proj_means_op %>% mutate(op = fct_reorder(op, Mean, 
                                         .fun = mean)) %>% 
  ggplot(aes(x = op, y=Mean, color = op)) +
  # coord_cartesian(ylim = c(0,1)) +
  geom_point(aes(shape = op), size = 4) + 
  scale_shape_manual(values = c("M", "N", "Q", "C")) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=0.1) +
  geom_line() + 
  labs(title = "Mean projectivity by operator")+
  theme_bw() +
  scale_color_brewer(palette = "PRGn")

proj_means_op %>% mutate(op = fct_reorder(op, Mean, 
                                         .fun = mean)) %>% 
  ggplot(aes(x = op, y=Mean, color = op, group = verb)) +
  # coord_cartesian(ylim = c(0,1)) +
  geom_point(aes(shape = op), size = 4) + 
  scale_shape_manual(values = c("M", "N", "Q", "C")) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=0.1) +
  facet_wrap(vars(verb)) +
  geom_line() + 
  labs(title = "Mean projectivity by operator")+
  theme_bw() +
  scale_color_brewer(palette = "PRGn")

@
\noindent The following generalizations emerge:
\begin{itemize}
  \item Conditionals have the highest projectivity ratings
  \item Projectivity ratings for questions are higher than those for modals and negation, but lower than those for conditionals
  \item Modals and negation have the lowest projectivity ratings
  \item The ratings for negation look a little higher than for modals, but error bars overlap
\end{itemize}

@@

\newpage
\subsection{Means and confidence intervals for projectivity rating by verb:}
<<summary-v, echo = FALSE, message=FALSE, cache=TRUE, fig.width=14, fig.height=7>>=

@@

\section{Analysis}

We are interested in how the response (projectivity ratings) depends on the verb and embedding operator.

<<>>=
# main analysis 4: predict projection from not-at-issueness, predicate, and their interaction ----

t = data_all %>% 
  mutate(verb = fct_relevel(verb, "suggest"))

m.dummy = lm(projective ~ ai*short_trigger, data=t)
summary(m.dummy)

# reference level set to "prove"

# model with short_trigger slope did not converge
m.4 = lmer(projective ~ cai*short_trigger + (1+cai|content) + (1+cai|workerid), 
           data = t, REML=F,control = lmerControl(optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
saveRDS(m.4, "../models/m.4.rds")
m.4 <- readRDS("../models/m.4.rds")
summary(m.4)
texreg(m.4,single.row = TRUE, leading.zero = FALSE, booktabs = TRUE)

<<>>=
formula <- response ~ op * verb
# formula <- response ~ op * verb + (1 | workerid) + (1 | item)
# formula <- response ~ op * verb + (1 + op + verb | workerid) + (1 + op + verb | item)
@

Trying a beta-regression. Our response variable has observations from a sliding scale between $(0,1)$. For beta regression, we rescale it to $[0,1]$, using method used in Degen \& Tonhauser (2022), from Smithson \& Verkuilen (2006).

<<>>=
data_all$response = (data_all$projective*(nrow(data_all)-1) + .5)/nrow(data_all)
@

<<>>=
# library(rstan)
# options(mc.cores=parallel::detectCores())
# rstan_options(auto_write=TRUE)
# library(brms)
# 
# model1 <- brm(formula = bf(response ~ op * verb ,
#                            phi ~ op * verb,
#                            family = Beta()),
#               family = Beta(),
#               data = data_all,
#               iter=10000, warmup=2000,chains=6)
